---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(ggeffects)
library(dplyr)
library(ggpubr)
library(grid)
library(lmerTest)
library(here)
i_am("Identity-Feedback.Rproj")
```

```{r}
library(devtools)
source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
```

```{r}
# fullLong1 <- data.table::fread("~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/id2traitDf.csv")
# orderDf1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/orderDf.csv")
# idShort1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/id2traitShort.csv")
# indDiff1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/indDiff.csv")
# idSim1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/identitySimDf.csv")

fullLong1 <- as.data.frame(arrow::read_parquet(here("Study 1","Data","id2traitDf.parquet")))
orderDf1 <- as.data.frame(arrow::read_parquet(here("Study 1","Data","orderDf.parquet")))
idShort1 <- as.data.frame(arrow::read_parquet(here("Study 1","Data","id2traitShort.parquet")))
indDiff1 <- as.data.frame(arrow::read_parquet(here("Study 1","Data","indDiff.parquet")))
idSim1 <-as.data.frame(arrow::read_parquet(here("Study 1","Data","identitySimDf.parquet")))


fullLong1$subTend <- as.numeric(fullLong1$subTend)
fullLong1$traitTend <- as.numeric(fullLong1$traitTend)
```

```{r}
fullLong1$Condition <- as.factor(fullLong1$Condition)

# create factor for race or not
fullLong1$RaceNo <- as.factor(ifelse(fullLong1$idcode==1, "Race", "notRace"))

# subset data for traits to only appear once per subject

traitsPerS1 <- fullLong1 %>% distinct(subID, Idx, .keep_all = TRUE)
#traitsPerS2 <- fullLong2 %>% distinct(subID, Idx, .keep_all = TRUE)

# convert to factors

fullLong1$connect <- as.factor(fullLong1$connect)
levels(fullLong1$connect) <- list(No  = "0", Yes = "1")

orderDf1$Condition <- as.factor(orderDf1$Condition)
levels(orderDf1$Condition) <- list(Control = "0", Feedback = "1")
fullLong1$Condition <- as.factor(fullLong1$Condition)
levels(fullLong1$Condition) <- list(Control = "0", Feedback = "1")
idShort1$Condition <- as.factor(idShort1$Condition)
levels(idShort1$Condition) <- list(Control = "0", Feedback = "1")

#fullLong2$connect <- as.factor(fullLong2$connect)
#levels(fullLong2$connect) <- list(No  = "0", Yes = "1")

# pos neg asymmetry

idShort1$pndiff <- idShort1$pI2Tdeg - idShort1$nI2Tdeg
#idShort2$pndiff <- idShort2$pI2Tdeg - idShort2$nI2Tdeg

RaceLong <- subset(fullLong1, idcode==1)

RaceOrder <- subset(orderDf1, idcode==1)

# subset data for only connected traits to appear per subject

connectDf1 <- fullLong1 %>% filter(connect=="Yes")
#connectDf2 <- fullLong2 %>% filter(connect==1)
```

```{r}
plotDf <- Rmisc::summarySE(data=fullLong1, groupvars=c("subID","connect","RaceNo","Condition"), measurevar="selfResp",na.r=T)
ggplot(data=plotDf, aes(x=connect, y=selfResp, color= as.factor(RaceNo), fill=as.factor(RaceNo) )) + geom_bar(stat="identity", position=position_dodge()) 

ggplot(plotDf, aes(RaceNo, selfResp, color=connect, fill = connect)) + 
  ggdist::stat_halfeye(adjust = .5, width = .7, .width = 0, justification = -.2, point_colour = NA, alpha = .3) +
  geom_boxplot(width = .2, outlier.shape = NA) + 
  geom_jitter(width = .05, alpha = .3) + labs(y="Proportion of Desirable Choices",x="Trial Type") + jtools::theme_apa() +
  facet_wrap(~Condition)# + 
  scale_color_manual(labels = c("Congruent", "Incongruent"), values = wes_palette("Chevalier1")) +
  scale_fill_manual(labels = c("Congruent", "Incongruent"), values = wes_palette("Chevalier1"))
```


# All traits

## Does an identity's distance from the impacted-racial identity relate to how self-descriptive the identity-connected traits is?

Identity-connected traits that are closer to impacted racial identity are evaluated more self-descriptively in feedback condition, while in control condition, identity-connected traits that are farther from impacted racial identity are evaluated more self-descriptively.

```{r}
propag.UW1 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*connect*Condition + scale(subTend) + scale(traitTend) + ( connect + scale(idDistRaceN) | subID / id ) + ( 1 | traits), data=fullLong1)
summary(propag.UW1)
```

Visualization

```{r}
m <- lmer( selfResp ~ idDistRaceN*connect*Condition + subTend + traitTend + ( connect + idDistRaceN | subID / id ) + ( 1 | traits), data=fullLong1)
propag.UW1.plot <- ggpredict(m, c("idDistRaceN","connect","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Racial Identity") + ylab("Self-Evaluation")
propag.UW1.plot
```

# How does stigma/stereotypes lead people to self-stereotype for more stereotype relevant traits?

```{r}
propag.Race.1 <- lmer(scale(selfResp) ~ scale(order)*Condition + ( scale(order) | subID ) + ( 1 | traits), data=RaceOrder)
summary(propag.Race.1)
ggpredict(propag.Race.1, c("order","Condition")) %>% plot()
```
Visualization

```{r}
m <- lmer(selfResp ~ order*Condition + ( order | subID ) + ( 1 | traits), data=RaceOrder)
summary(m)
ggpredict(m, c("order","Condition")) %>% plot(show.title = F) + jtools::theme_apa() + xlab("Trait Distance from Racial Identity") + ylab("Self-Evaluation")
```


```{r}
propag.Race.1 <- lmer(scale(selfResp) ~ scale(T.Sim)*Condition + ( scale(T.Sim) | subID ) + ( 1 | traits), data=RaceOrder)
summary(propag.Race.1)
ggpredict(propag.Race.1, c("T.Sim","Condition")) %>% plot()
```

```{r}
propag.Race.1 <- lmer(scale(selfResp) ~ scale(order)*Condition*valence + ( scale(order) | subID ) + ( 1 | traits), data=RaceOrder)
summary(propag.Race.1)
ggpredict(propag.Race.1, c("order","Condition")) %>% plot()
```


# How does stigma/stereotypes lead people to self-stereotype for more stereotype relevant traits? Particularly for strongly identified individuals?

```{r}
propag.Race.Id.1 <- lmer(scale(selfResp) ~ scale(order)*Condition*IdImp + idNum + ( scale(order) | subID ) + ( 1 | traits), data=RaceOrder)
summary(propag.Race.Id.1)
```

Visualization

```{r}
m <- lmer(selfResp ~ order*Condition*IdImp + ( order | subID ) + ( 1 | traits), data=RaceOrder)
summary(m)
ggpredict(m, c("order","IdImp","Condition")) %>% plot(show.title = F) + jtools::theme_apa() + scale_color_discrete(labels = c("Low Identification", "Medium Identification", "High Identification")) + xlab("Trait Distance from Racial Identity") + ylab("Self-Evaluation")
```

```{r}
propag.Race.1 <- lmer(scale(selfResp) ~ scale(order)*Condition + ( scale(order) + valence | subID ) + ( 1 | traits), data=RaceOrder)
summary(propag.Race.1)
ggpredict(propag.Race.1, c("order","valence","Condition")) %>% plot()
```

```{r}
propag.Race.1 <- lmer(scale(selfResp) ~ scale(order)*Condition + ( scale(order) | subID ) + ( 1 | traits), data=RaceOrder)
summary(propag.Race.1)
ggpredict(propag.Race.1, c("order","Condition")) %>% plot()
```



## Does an identity's distance from the impacted-racial identity relate to how self-descriptive farther or closer traits are?

Identity-connected traits that are closer to impacted racial identity are evaluated more self-descriptively in feedback condition, while in control condition, identity-connected traits that are farther from impacted racial identity are evaluated more self-descriptively.

```{r}
propag.UW2 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*scale(order)*Condition + scale(subTend) + scale(traitTend) + ( scale(order) + scale(idDistRaceN) | subID / id ) + ( 1 | traits), data=orderDf1)
summary(propag.UW2)
```

Visualization

```{r}
m <- lmer( selfResp ~ idDistRaceN*order*Condition + subTend + traitTend + ( order + idDistRaceN | subID / id ) + ( 1 | traits), data=orderDf1)
propag.UW2.plot <- ggpredict(m, c("idDistRaceN","order","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Racial Identity") + ylab("Self-Evaluation")
propag.UW2.plot
```

## Does an identity's distance from the impacted-racial identity relate to how self-descriptive identity-similar traits are?

```{r}
propag.UW3 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*scale(T.Sim)*Condition + scale(subTend) + scale(traitTend) + ( scale(T.Sim) + scale(idDistRaceN) | subID / id ) + ( 1 | traits), data=orderDf1)
summary(propag.UW3)
```

Visualization

```{r}
m <- lmer( selfResp ~ idDistRaceN*T.Sim*Condition + subTend + traitTend + ( T.Sim + idDistRaceN | subID / id ) + ( 1 | traits), data=orderDf1)
propag.UW3.plot <- ggpredict(m, c("idDistRaceN","T.Sim","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Racial Identity") + ylab("Self-Evaluation")
propag.UW3.plot
```
## Does an identity's similarity to the impacted-racial identity relate to how self-descriptive the identity-connected traits is?

Traits that are more similar to the impacted racial identity are evaluated more self-descriptively.

```{r}
propag.W1 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*connect*Condition + scale(subTend) + scale(traitTend) + ( connect + scale(idDistRaceNW) | subID / id ) + ( 1 | traits), data=fullLong1)
summary(propag.W1)
```

Visualization

```{r}
m <- lmer( selfResp ~ idDistRaceNW*connect*Condition + subTend + traitTend + ( connect + idDistRaceNW | subID / id ) + ( 1 | traits), data=fullLong1)
propag.W1.plot <- ggpredict(m, c("idDistRaceNW","connect","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Similarity to Racial Identity") + ylab("Self-Evaluation")
propag.W1.plot
```


## Does an identity's distance from the impacted-racial identity relate to how self-descriptive farther or closer traits are?

Identity-connected traits that are closer to impacted racial identity are evaluated more self-descriptively in feedback condition, while in control condition, identity-connected traits that are farther from impacted racial identity are evaluated more self-descriptively.

```{r}
propag.W2 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*scale(order)*Condition + scale(subTend) + scale(traitTend) + ( scale(order) + scale(idDistRaceNW) | subID / id ) + ( 1 | traits), data=orderDf1)
summary(propag.W2)
```

Visualization

```{r}
m <- lmer( selfResp ~ idDistRaceNW*order*Condition + subTend + traitTend + ( order + idDistRaceNW | subID / id ) + ( 1 | traits), data=orderDf1)
propag.W2.plot <- ggpredict(propag.W2, c("idDistRaceNW","order","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity Similarity to Impacted Racial Identity") + ylab("Self-Evaluation")
propag.W2.plot
```

## Does an identity's distance from the impacted-racial identity relate to how self-descriptive identity similar traits are?

```{r}
propag.W3 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*scale(T.Sim)*Condition + scale(subTend) + scale(traitTend) + ( scale(T.Sim) + scale(idDistRaceNW) | subID / id ) + ( 1 | traits), data=orderDf1)
summary(propag.W3)
```

Visualization

```{r}
m <- lmer( selfResp ~ idDistRaceNW*T.Sim*Condition + subTend + traitTend + ( T.Sim + idDistRaceNW | subID / id ) + ( 1 | traits), data=orderDf1)
propag.W3.plot <- ggpredict(m, c("idDistRaceNW","T.Sim","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity Similarity to Impacted Racial Identity") + ylab("Self-Evaluation")
propag.W3.plot
```

# Connected Traits Only for Full Dataset

## Are connected traits more affected for racial identity than non-racial identity by feedback?

Small--

```{r}
connect1 <- lmer( scale(selfResp) ~ Condition*RaceNo  + scale(subTend) + scale(traitTend) + ( RaceNo | subID ) + ( 1 | traits), data=connectDf1)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","RaceNo")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Condition") + ylab("Self-Evaluation")
connect1.plot
```

## Are there valence-differences in how connected traits more affected for racial identity than non-racial identity by feedback?

Nope

```{r}
connect1 <- lmer( scale(selfResp) ~ Condition*RaceNo*valence  + scale(subTend) + scale(traitTend) + ( RaceNo + valence | subID ) + ( 1 | traits), data=connectDf1)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","RaceNo","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Condition") + ylab("Self-Evaluation")
connect1.plot
```

# Racial Identity Dataframe Only

## Do people self-endorse more for race-connected traits due to feedback?

nah

```{r}
connect1 <- lmer(scale(selfResp) ~ connect*Condition + identity  + scale(subTend) + scale(traitTend) + ( connect | subID ) + ( 1 | traits), data=RaceLong)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","connect")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Condition") + ylab("Self-Evaluation")
connect1.plot
```

```{r}
connect1 <- lmer(scale(selfResp) ~ connect*Condition*valence + identity  + scale(subTend) + scale(traitTend) + ( connect + valence | subID ) + ( 1 | traits), data=RaceLong)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","connect","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Condition") + ylab("Self-Evaluation")
connect1.plot
```

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(order)*Condition*valence + identity  + scale(subTend) + scale(traitTend) + ( scale(order) * valence | subID ) + ( 1 | traits), data=orderDf1[orderDf1$idcode==1,])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("order","Condition","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Racial Identity") + ylab("Self-Evaluation")
connect1.plot
```

## Do people self-endorse more for race connected traits, depending on valence?

People are more self-descriptive on connected positive traits in feedback condition than control condition, while no such differences exist for negative traits.

```{r}
connect1.v <- lmer(scale(selfResp) ~ connect*Condition*valence + identity  + scale(subTend) + scale(traitTend) + ( connect + valence | subID ) + ( 1 | traits), data=RaceLong)
summary(connect1.v)
connect1.v.plot <- ggpredict(connect1.v, c("Condition","connect","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Condition") + ylab("Self-Evaluation")
connect1.v.plot
```

# Race-Connected Traits

## Is there an effect of feedback on race-connected traits?

Nah

```{r}
sconnect1 <- lmer(scale(selfResp) ~ Condition + scale(subTend) + scale(traitTend) + ( 1 | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(sconnect1)
sconnect1.plot <- ggpredict(connect1, c("Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
sconnect1.plot
```

## Does the effect of condition on race-connected traits depend on valence?

```{r}
sconnect1.v <- lmer(scale(selfResp) ~ Condition*valence + scale(subTend) + scale(traitTend) + ( valence | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(sconnect1.v)
sconnect1.v.plot <- ggpredict(connect1.v, c("Condition","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
sconnect1.v.plot
```

## Does the effect of feedback on race-connected traits depend on valence and identity-positivity?

People with more positively perceived racial identities self-enhance on racial-relevant traits more after feedback.

```{r}
connect1 <- lmer(scale(selfResp) ~ Condition*scale(pos)*valence + scale(subTend) + scale(traitTend) + ( scale(pos) + valence | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("pos","Condition","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity Positivity") + ylab("Self-Evaluation")
connect1.plot
```

## Does the effect of feedback on race-connected traits depend on valence and strength of identification?

nah

```{r}
connect1 <- lmer(scale(selfResp) ~ Condition*scale(streng)*valence + scale(subTend) + scale(traitTend) + ( scale(streng) + valence | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("streng","Condition","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Strength of Identification") + ylab("Self-Evaluation")
connect1.plot
```

```{r}
m <- lmer(scale(pos) ~ scale(idDistRaceNW) * Condition + ( scale(idDistRaceNW) | subID), data=idShort1)
summary(m)
```


# Self-endorsing identity-typical traits leads to greater identification/perceived positivity?

```{r}
RaceLong$connectn <- as.numeric(RaceLong$connect)-1
summarized <- Rmisc::summarySE(data=RaceLong, measurevar = "selfResp", groupvars = c("subID","connect"))

summarized<-tidyr::pivot_wider(summarized, id_cols="subID", values_from="selfResp",names_from="connect")
# 
# summarized <- merge(summarized, indDiff1, by="subID")

RaceShort <- RaceLong[match(unique(RaceLong$subID), RaceLong$subID),]

summarized <- merge(summarized, RaceShort, by="subID")

# more self-descriptive on race-connected relative to race-unconnected traits
summarized$diff <- summarized$Yes-summarized$No

m <- lm(diff ~ Condition * pos, data=summarized)
summary(m)
ggpredict(m, c("pos","Condition")) %>% plot(show.title=FALSE) 

m <- lm(inclus ~ Condition * diff, data=summarized)
summary(m)

m <- lm(streng ~ Condition * diff, data=summarized)
summary(m)

m <- lm((SE.T2-SE.T1) ~ Condition * diff, data=summarized)
summary(m)

summarized$MGIS.Diff <- (summarized$MGIS.T2-summarized$MGIS.T1)
m <- lm(MGIS.Diff ~ Condition * diff, data=summarized)
summary(m)
ggpredict(m, c("diff","Condition")) %>% plot(show.title=FALSE) 
ggpredict(m, c("Condition")) %>% plot(show.title=FALSE) 

m <- lm((PANAS_Pos.T2-PANAS_Pos.T1) ~ Condition * diff, data=summarized)
summary(m)

m <- lm((PANAS_Neg.T2-PANAS_Neg.T1) ~ Condition * diff, data=summarized)
summary(m)
```

# Does negative feedback propagate to influence perceived positivity of connected identities?

```{r}
connect2 <- lmer(scale(pos) ~ Condition * idCommRaceN + ( idCommRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idCommRaceN","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(stig) ~ Condition * idCommRaceN + ( idCommRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idCommRaceN","Condition")) %>% plot(show.title=FALSE)

connect2 <- lmer(scale(streng) ~ Condition * scale(idCommRaceN) + idNum + ( scale(idCommRaceN) | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idCommRaceN","Condition")) %>% plot(show.title=FALSE)  + jtools::theme_apa() + xlab("Similarity to Racial Identity") + ylab("Strength of Identification")
```


```{r}
connect2 <- lmer(scale(pos) ~ Condition * traitCommRaceN + ( traitCommRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("traitCommRaceN","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(stig) ~ Condition * traitCommRaceN + ( traitCommRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("traitCommRaceN","Condition")) %>% plot(show.title=FALSE)

connect2 <- lmer(scale(streng) ~ Condition * traitCommRaceN + idNum + ( traitCommRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("traitCommRaceN","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Racial Identity") + ylab("Self-Evaluation")
```

```{r}
connect2 <- lmer(scale(pos) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(stig) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE)

connect2 <- lmer(scale(streng) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE)
```


## Exploratory Identity Propagation Models

```{r}
connect2 <- lmer(scale(streng) ~ Condition * idDistRaceN + ( idDistRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(sizeS) ~ Condition * idDistRaceN + ( idDistRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(sizeU) ~ Condition * idDistRaceN + ( idDistRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(inclus) ~ Condition * idDistRaceN + ( idDistRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(differ) ~ Condition * idDistRaceN + ( idDistRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 
```

```{r}
m <- connect2 <- lmer(scale(streng) ~ Condition * traitCommRaceN + Condition * idCommRaceN + ( traitCommRaceN + idCommRaceN | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)

shortestDf <- idShort1[!duplicated(idShort1$subID),]
m <- lm((SE.T2-SE.T1)~traitCommRaceM*Condition + idCommRaceM*Condition, data=shortestDf)
summary(m)

m <- lm(SE.T2~traitCommRaceM*Condition + SE.T1, data=shortestDf)
summary(m)


m <- lm(SCS.T2~traitCommRaceM*Condition + SCS.T1 + idNum, data=shortestDf)
summary(m)
ggpredict(m, c("traitCommRaceM","Condition")) %>% plot(show.title=FALSE) 

m <- lm(MGIS.T2~traitCommRaceM*Condition + MGIS.T1 + idNum, data=shortestDf)
summary(m)
ggpredict(m, c("traitCommRaceM","Condition")) %>% plot(show.title=FALSE) 

m <- lm(PANAS_Pos.T2~traitCommRaceM*Condition + PANAS_Pos.T1 + idNum, data=shortestDf)
summary(m)
ggpredict(m, c("traitCommRaceM","Condition")) %>% plot(show.title=FALSE) 

m <- lm(PANAS_Neg.T2~traitCommRaceM*Condition + PANAS_Neg.T1 + idNum, data=shortestDf)
summary(m)
ggpredict(m, c("traitCommRaceM","Condition")) %>% plot(show.title=FALSE) 

m <- lm(PANAS_Neg.T2~traitCommRaceM*Condition + PANAS_Neg.T1 + idNum, data=shortestDf)
summary(m)
ggpredict(m, c("traitCommRaceM","Condition")) %>% plot(show.title=FALSE) 
```


# Does feedback propagate to influence self-descriptiveness for identity connected vs. non identity connected traits?

Self-descriptiveness of connected relative to non-connected traits... As you get farther from the racial identity, connected traits become less self-descriptive.

```{r}
fullLong1$connectn <- as.numeric(fullLong1$connect)-1
summarized <- Rmisc::summarySE(data=fullLong1, measurevar = "selfResp", groupvars = c("subID","idcode","connect"), na.rm=T)

summarized<-tidyr::pivot_wider(summarized, id_cols=c("subID","idcode"), values_from="selfResp",names_from="connect")

shortened <- fullLong1[match(unique(fullLong1$subID), fullLong1$subID),]

summarized <- merge(summarized, idShort1, by=c("subID","idcode"))

summarized$diff <- summarized$Yes-summarized$No

endorseprop <- lmer(scale(diff) ~ Condition * idDistRaceN + ( idDistRaceN | subID ) + ( 1 | idcode), data=summarized)
summary(endorseprop)
ggpredict(endorseprop, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 


endorseprop <- lmer(scale(diff) ~ Condition * scale(idCommRaceN) + ( scale(idCommRaceN) | subID ) + ( 1 | idcode), data=summarized)
summary(endorseprop)
ggpredict(endorseprop, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 
```

# Does identity spillover to shape self-descriptiveness for connected identities and traits?

Traits connected to racial identity are evaluated more self-descriptively that non-connected traits.

```{r}
fullLong1$raceyn <- ifelse(fullLong1$idcode==1, "Racial", "Not")
connect1 <- lmer(scale(selfResp) ~ raceyn*connect*Condition + scale(subTend) + scale(traitTend) + ( connect + raceyn | subID ) + ( 1 | traits), data=fullLong1)
summary(connect1)
ggpredict(connect1, c("Condition","raceyn","connect")) %>% plot(show.title=FALSE) 
```

```{r}
# Fill in other analyses here
```

# Feedback influences self-views for identities more overlapping with affected racial identity?

Self-evaluations for identities farther from 

```{r}
connectedLong <- subset(fullLong1, connect == "Yes")
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*Condition + scale(subTend) + scale(traitTend) + ( scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceN","Condition")) %>% plot(show.title=FALSE) 
```

# Depends on valence?

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*Condition*valence + scale(subTend) + scale(traitTend) + ( valence + scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition","valence")) %>% plot(show.title=FALSE) 
```

## Depends on overlap between identities?

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*Condition*overlap_norm + scale(subTend) + scale(traitTend) + ( overlap_norm + scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition","overlap_norm")) %>% plot(show.title=FALSE) 
```

## Depends on strength of perceived positivity of identity?

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*Condition*pos + scale(subTend) + scale(traitTend) + ( scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition","overlap_norm")) %>% plot(show.title=FALSE) 
```

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceN)*Condition*valence + scale(subTend) + scale(traitTend) + ( scale(idDistRaceN) + valence  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
```

# Similarity Analyses

```{r}
sim.m1 <- lmer(scale(strengDist) ~ scale(idSim)*Condition + ( scale(idSim) | subID ), data=idSim1)
summary(sim.m1)
```

```{r}
sim.m1 <- lmer(scale(strengDist) ~ scale(idSim)*Condition*raceConn + ( scale(idSim) | subID ), data=idSim1)
summary(sim.m1)
ggpredict(sim.m1, c("idSim","Condition","raceConn")) %>% plot(show.title=FALSE) 
```

$

```{r}
dist.m1 <- lmer(scale(selfResp) ~ scale(order)*Condition + ( scale(order) | subID ) + (1 | traits), data=orderDf1)
summary(dist.m1)
```

```{r}
raceOrder <- subset(orderDf1, idq == identity)
dist.m1 <- lmer(scale(selfResp) ~ scale(IT.Sim)*Condition + ( scale(order) | subID ) + (1 | traits), data=raceOrder)
summary(dist.m1)
ggpredict(dist.m1, c("IT.Sim","Condition")) %>% plot(show.title=FALSE) 
```


