---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(ggeffects)
library(dplyr)
library(ggpubr)
library(grid)
library(lmerTest)
```

```{r}
library(devtools)
source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
```

```{r}
fullLong1 <- data.table::fread("~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/id2traitDf.csv")
orderDf1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/orderDf.csv")
idShort1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/id2traitShort.csv")
indDiff1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/indDiff.csv")
idSim1 <- data.table::fread( "~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/identitySimDf.csv")
```

```{r}
# subset data for traits to only appear once per subject

traitsPerS1 <- fullLong1 %>% distinct(subID, Idx, .keep_all = TRUE)
#traitsPerS2 <- fullLong2 %>% distinct(subID, Idx, .keep_all = TRUE)

# subset data for only connected traits to appear per subject

connectDf1 <- fullLong1 %>% filter(connect==1)
#connectDf2 <- fullLong2 %>% filter(connect==1)

# convert to factors

fullLong1$connect <- as.factor(fullLong1$connect)
levels(fullLong1$connect) <- list(No  = "0", Yes = "1")

fullLong1$Condition <- as.factor(fullLong1$Condition)
levels(fullLong1$Condition) <- list(Control = "0", Feedback = "1")
idShort1$Condition <- as.factor(idShort1$Condition)
levels(idShort1$Condition) <- list(Control = "0", Feedback = "1")

#fullLong2$connect <- as.factor(fullLong2$connect)
#levels(fullLong2$connect) <- list(No  = "0", Yes = "1")

# pos neg asymmetry

idShort1$pndiff <- idShort1$pI2Tdeg - idShort1$nI2Tdeg
#idShort2$pndiff <- idShort2$pI2Tdeg - idShort2$nI2Tdeg

RaceLong <- subset(fullLong1, idcode==1)
```

# Do people self-endorse more for race connected traits?

```{r}
connect1 <- lmer(scale(selfResp) ~ connect*Condition + scale(subTend) + scale(traitTend) + identity + ( connect | subID ) + ( 1 | traits), data=RaceLong)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","connect")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```

## Only looking at connected traits

```{r}
connect1 <- lmer(scale(selfResp) ~ Condition + scale(subTend) + scale(traitTend) + ( 1 | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","pos","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```

## Only looking at connected traits, moderated by valence

```{r}
connect1 <- lmer(scale(selfResp) ~ Condition*valence + scale(subTend) + scale(traitTend) + ( 1 | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","pos","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```
## Only looking at connected traits, moderated by valence and positivity of identity

```{r}
connect1 <- lmer(scale(selfResp) ~ Condition*pos*valence + scale(subTend) + scale(traitTend) + ( pos + valence | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","pos","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```

## Only looking at connected traits, moderated by valence and strength of identification

```{r}
connect1 <- lmer(scale(selfResp) ~ Condition*streng*valence + scale(subTend) + scale(traitTend) + ( streng | subID ) + ( 1 | traits), data=RaceLong[RaceLong$connect=="Yes",])
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","pos","valence")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```

### Does it depend on valence?

```{r}
connectval1 <- lmer(scale(selfResp) ~ connect*Condition*valence + scale(subTend) + scale(traitTend) + ( connect + valence | subID ) + ( 1 | traits), data=RaceLong)
summary(connectval1)
connectval1.plot <- ggpredict(connectval1, c("valence","connect","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connectval1.plot
```

```{r}
connectval1 <- lmer(scale(selfResp) ~ connect*Condition*valence + scale(subTend) + scale(traitTend) + ( connect + valence | subID ) + ( 1 | traits), data=RaceLong)
summary(connectval1)
connectval1.plot <- ggpredict(connectval1, c("valence","connect","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connectval1.plot
```


```{r}
connectval1 <- lmer(scale(selfResp) ~ connect*Condition*idDistRaceNW + scale(subTend) + scale(traitTend) + ( connect + valence | subID ) + ( 1 | traits), data=RaceLong)
summary(connectval1)
connectval1.plot <- ggpredict(connectval1, c("valence","connect","Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connectval1.plot
```



```{r}
connect1 <- lmer(scale(selfResp) ~ as.factor(connect)*as.factor(Condition)*overlap_norm + scale(subTend) + scale(traitTend) + ( connect | subID ) + ( 1 | traits), data=fullLong1)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","connect","overlap_norm")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```

```{r}
connect1 <- lmer(scale(selfResp) ~ idDistRaceNW*connect*as.factor(Condition) + scale(subTend) + scale(traitTend) + ( connect | subID ) + ( 1 | traits), data=fullLong1)
summary(connect1)
connect1.plot <- ggpredict(connect1, c("Condition","connect","idDistRaceNW")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect1.plot
```
# Self-endorsing identity-typical traits leads to greater identification/perceived positivity?

```{r}
RaceLong$connectn <- as.numeric(RaceLong$connect)-1
summarized <- Rmisc::summarySE(data=RaceLong, measurevar = "selfResp", groupvars = c("subID","connect"))

summarized<-tidyr::pivot_wider(summarized, id_cols="subID", values_from="selfResp",names_from="connect")
# 
# summarized <- merge(summarized, indDiff1, by="subID")

RaceShort <- RaceLong[match(unique(RaceLong$subID), RaceLong$subID),]

summarized <- merge(summarized, RaceShort, by="subID")

summarized$diff <- summarized$Yes-summarized$No

m <- lm(diff ~ as.factor(Condition) * pos, data=summarized)
summary(m)
ggpredict(m, c("pos","Condition")) %>% plot(show.title=FALSE) 

m <- lm(inclus ~ as.factor(Condition) * diff, data=summarized)
summary(m)

m <- lm(streng ~ as.factor(Condition) * diff, data=summarized)
summary(m)

m <- lm((SE.T2-SE.T1) ~ as.factor(Condition) * diff, data=summarized)
summary(m)

m <- lm((MGIS.T2-MGIS.T1) ~ as.factor(Condition) * diff, data=summarized)
summary(m)

m <- lm((PANAS_Pos.T2-PANAS_Pos.T1) ~ as.factor(Condition) * diff, data=summarized)
summary(m)

m <- lm((PANAS_Neg.T2-PANAS_Neg.T1) ~ as.factor(Condition) * diff, data=summarized)
summary(m)
```

# Does negative feedback propagate to influence perceived positivity of connected identities?

```{r}
connect2 <- lmer(scale(pos) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(stig) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE)
```

## Exploratory Identity Propagation Models

```{r}
connect2 <- lmer(scale(streng) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(sizeS) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(sizeU) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(inclus) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 

connect2 <- lmer(scale(differ) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=idShort1)
summary(connect2)
ggpredict(connect2, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 
```

# Does feedback propagate to influence self-descriptiveness for identity connected vs. non identity connected traits?

```{r}
fullLong1$connectn <- as.numeric(fullLong1$connect)-1
summarized <- Rmisc::summarySE(data=fullLong1, measurevar = "selfResp", groupvars = c("subID","idcode","connect"), na.rm=T)

summarized<-tidyr::pivot_wider(summarized, id_cols=c("subID","idcode"), values_from="selfResp",names_from="connect")

shortened <- fullLong1[match(unique(fullLong1$subID), fullLong1$subID),]

summarized <- merge(summarized, idShort, by=c("subID","idcode"))

summarized$diff <- summarized$Yes-summarized$No

endorseprop <- lmer(scale(diff) ~ Condition * idDistRaceNW + ( idDistRaceNW | subID ) + ( 1 | idcode), data=summarized)
summary(endorseprop)
ggpredict(endorseprop, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 
```

# Does identity spillover to shape self-descriptiveness for connected identities and traits?

```{r}
fullLong1$raceyn <- ifelse(fullLong1$idcode==1, "Racial", "Not")
connect1 <- lmer(scale(selfResp) ~ raceyn*connect*Condition + scale(subTend) + scale(traitTend) + ( connect | subID ) + ( 1 | traits), data=fullLong1)
summary(connect1)
ggpredict(connect1, c("Condition","raceyn","connect")) %>% plot(show.title=FALSE) 
```

```{r}
# Fill in other analyses here
```

# Feedback influences self-views for identities more overlapping with affected racial identity?

```{r}
connectedLong <- subset(fullLong1, connect == "Yes")
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*Condition + scale(subTend) + scale(traitTend) + ( scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition")) %>% plot(show.title=FALSE) 
```

# Depends on valence?

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*Condition*valence + scale(subTend) + scale(traitTend) + ( valence + scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition","valence")) %>% plot(show.title=FALSE) 
```

## Depends on overlap between identities?

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*Condition*overlap_norm + scale(subTend) + scale(traitTend) + ( overlap_norm + scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition","overlap_norm")) %>% plot(show.title=FALSE) 
```

## Depends on strength of perceived positivity of identity?

```{r}
connect1 <- lmer(scale(selfResp) ~ scale(idDistRaceNW)*Condition*pos + scale(subTend) + scale(traitTend) + ( scale(idDistRaceNW)  | subID ) + ( 1 | traits), data=connectedLong)
summary(connect1)
ggpredict(connect1, c("idDistRaceNW","Condition","overlap_norm")) %>% plot(show.title=FALSE) 
```


## Study 2

```{r}
connect2 <- lmer(scale(selfResp) ~ connect + subTend + traitTend + ( connect | subID ) + ( 1 | traits), data=fullLong2)
summary(connect2)
connect2.plot <- ggpredict(connect2, c("connect")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Typicality") + ylab("Self-Evaluation")
connect2.plot
```

## Combined

```{r}
plotCommAxes(connect1.plot, connect2.plot, "Connect", "Self-Evaluation")
```

# Effect of Identity Typicality Depends on Identity Importance

## Study 1

Identity importance defined by strength of identification. This is not significant for identity-to-identity centrality.

```{r}
connect.streng1 <- lmer(scale(selfResp) ~ connect * scale(streng) + subTend + traitTend + ( connect + scale(streng) | subID ) + ( 1 | traits), data=fullLong1)
summary(connect.streng1)
connect.streng1.plot <- ggpredict(connect.streng1, c("streng","connect")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Strength of Identification") + ylab("Self-Evaluation")
connect.streng1.plot
```

## Study 2

```{r}
connect.streng2 <- lmer(scale(selfResp) ~ connect * scale(streng) + ( connect + scale(streng) | subID ) + ( 1 | traits), data=fullLong2)
summary(connect.streng2)
connect.streng2.plot <- ggpredict(connect.streng2, c("streng","connect")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Strength of Identification") + ylab("Self-Evaluation")
connect.streng2.plot
```

## Combined

```{r}
plotCommAxes(connect.streng1.plot, connect.streng2.plot, "Strength of Identification", "Self-Evaluation")
```

# Effect of Identity Typicality Depends on Size

## Size Difference

```{r}
connect.size2 <- lmer(scale(selfResp) ~ connect * scale(sizeD) + ( connect + scale(sizeD) | subID ) + ( 1 | traits), data=fullLong2)
summary(connect.size2)
connect.size2.plot <- ggpredict(connect.size2, c("sizeD","connect")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Size Differences") + ylab("Self-Evaluation")
connect.size2.plot
```

# Identity Connections

Traits that are nominated as typical of more identities are evaluated more self-descriptively

## Study 1

```{r}
moconn1 <- lmer(scale(selfResp) ~ scale(IdIn) + ( scale(IdIn) | subID ) + ( 1 | traits), data=traitsPerS1)
summary(moconn1)
moconn1.plot <- ggpredict(moconn1, c("IdIn")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Associations") + ylab("Self-Evaluation")
moconn1.plot
```


## Study 2

```{r}
moconn2 <- lmer(scale(selfResp) ~ scale(IdIn) + ( scale(IdIn) | subID ) + ( 1 | traits), data=traitsPerS1)
summary(moconn2)
moconn2.plot <- ggpredict(moconn2, c("IdIn")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-Associations") + ylab("Self-Evaluation")
moconn2.plot
```

## Combined

```{r}
plotCommAxes(moconn1.plot, moconn2.plot, "Identity-Typicality", "Self-Evaluation")
```

# Identity Overlap

## Study 1

```{r}
sm1<-lmer(scale(selfResp) ~ scale(T.Sim) * scale(streng) + scale(subTend) + scale(traitTend)   + ( scale(T.Sim) | subID ) + ( 1 | traits), data=orderDf1, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
summary(sm1)
sm1.plot <- ggpredict(sm1, c("T.Sim", "streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Overlap with Identity") + ylab("Self-Evaluation")
sm1.plot
```

## Study 2

```{r}
sm2<-lmer(scale(selfResp) ~ scale(T.Sim) * scale(streng) + scale(subTend) + scale(traitTend)  + ( scale(T.Sim) | subID ) + ( 1 | traits), data=orderDf2, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
summary(sm2)
sm2.plot <- ggpredict(sm2, c("T.Sim", "streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Overlap with Identity") + ylab("Self-Evaluation")
sm2.plot
```

## Combined Plot

```{r}
plotCommAxes(sm1.plot, sm2.plot, "Identity Overlap", "Self-Evaluation")
```

# Identity Distance

## Study 1

```{r}
orderRace <- subset(orderDf1, idcode==1)
dm1<-lmer(scale(selfResp) ~ scale(order) * as.factor(Condition) * scale(streng) + scale(subTend) + scale(traitTend)  + ( scale(order) | subID ) + ( 1 | traits), data=orderDf1)
summary(dm1)
dm1.plot <- ggpredict(dm1, c("order","streng", "Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Identity") + ylab("Self-Evaluation")
dm1.plot
```

```{r}
orderRace <- subset(orderDf1, idcode==1)
dm1<-lmer(scale(selfResp) ~ scale(order) * as.factor(Condition) * scale(stig) + scale(subTend) + scale(traitTend)  + ( scale(order) | subID ) + ( 1 | traits), data=orderDf1)
summary(dm1)
dm1.plot <- ggpredict(dm1, c("order","stig", "Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Identity") + ylab("Self-Evaluation")
dm1.plot
```

```{r}
orderRace <- subset(orderDf1, idcode==1)
dm1<-lmer(scale(selfResp) ~ scale(order) * as.factor(Condition) * scale(OD) + scale(subTend) + scale(traitTend)  + ( scale(order) | subID ) + ( 1 | traits), data=orderDf1)
summary(dm1)
dm1.plot <- ggpredict(dm1, c("order","OD", "Condition")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Identity") + ylab("Self-Evaluation")
dm1.plot
```

## Study 2

```{r}
dm2<-lmer(scale(selfResp) ~ scale(order) * scale(streng) + scale(subTend) + scale(traitTend)  + ( scale(order) | subID ) + ( 1 | traits), data=orderDf2)
summary(dm2)
dm2.plot <- ggpredict(dm2, c("order", "streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Distance from Identity") + ylab("Self-Evaluation")
dm2.plot
```

## Combined Plot

```{r}
plotCommAxes(dm1.plot, dm2.plot, "Identity Distance", "Self-Evaluation")
```

# Identity Similarity and Distance Joint Influence on Self-Evaluations (Principal Component)

## Study 1

```{r}
pca1<-lmer(scale(selfResp) ~ scale(PCAdist) * scale(streng) + scale(subTend) + scale(traitTend) + ( scale(PCAdist) | subID ) + ( 1 | traits), data=orderDf1)
summary(pca1)
pca1.plot <- ggpredict(pca1, c("PCAdist", "streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Composite Identity-Overlap") + ylab("Self-Evaluation")
pca1.plot
```

## Study 2

```{r}
pca2<-lmer(scale(selfResp) ~ scale(PCAdist) * scale(streng) + scale(subTend) + scale(traitTend) + ( scale(PCAdist) | subID ) + ( 1 | traits), data=orderDf2)
summary(pca2)
pca2.plot <- ggpredict(pca2, c("PCAdist", "streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Composite Identity-Overlap") + ylab("Self-Evaluation")
pca2.plot
```

## Combined Plot

```{r}
plotCommAxes(pca1.plot, pca2.plot, "Composite Identity-Overlap", "Self-Evaluation")
```

# Identity Centrality Predicts Strength of Identification

## Study 1

```{r}
I2I1.streng<-lmer(scale(streng) ~ scale(I2Ideg) + ( scale(I2Ideg) | subID ) + ( 1 | id), data=idShort1)
summary(I2I1.streng)
I2I1.streng.plot <- ggpredict(I2I1.streng, c("I2Ideg")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-to-Identity Centrality") + ylab("Self-Evaluation")
I2I1.streng.plot
```

## Study 2

```{r}
I2I2.streng<-lmer(scale(streng) ~ scale(I2Ideg) + ( scale(I2Ideg) | subID ) + ( 1 | id), data=idShort2)
summary(I2I2.streng)
I2I2.streng.plot <- ggpredict(I2I2.streng, c("I2Ideg")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Identity-to-Identity Centrality") + ylab("Self-Evaluation")
I2I2.streng.plot
```

## Combined Plot

```{r}
plotCommAxes(I2I1.streng.plot, I2I2.streng.plot, "Identity-to-Identity Centrality", "Strength of Identification")
```

# Strength of Identification Predicts More Shared Traits Between Identities

## Study 1

```{r}
TSharedStreng1 <- lmer( scale(traitCommNod) ~ scale(streng) + ( scale(streng)  | subID) + ( 1 | id), data=idShort1)
summary(TSharedStreng1)
TSharedStreng1.plot <- ggpredict(TSharedStreng1, c("streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Strength of Identification") + ylab("Shared Traits")
```

## Study 2

```{r}
TSharedStreng2 <- lmer( scale(traitCommNod) ~ scale(streng) + ( scale(streng)  | subID) + ( 1 | id), data=idShort2)
summary(TSharedStreng2)
TSharedStreng2.plot <- ggpredict(TSharedStreng2, c("streng")) %>% plot(show.title=FALSE) + jtools::theme_apa() + xlab("Strength of Identification") + ylab("Shared Traits")
```

## Combined Plot

```{r}
ggpubr::ggarrange(TSharedStreng1.plot, TSharedStreng2.plot)
plotCommAxes(TSharedStreng1.plot, TSharedStreng2.plot, "Strength of Identification", "Proportion of Traits in Common")
```

# Does positvity of identity predict asymmetries in valenced content?

## Study 1

```{r}
asym.pos1 <-lmer(pos ~ pndiff + ( pndiff | subID) + (1 | id), data=idShort1)
summary(asym.pos1)
```

## Study 2

```{r}
asym.pos2 <-lmer(pos ~ pndiff + ( pndiff | subID) + (1 | id), data=idShort2)
summary(asym.pos2)
```

# More trait overlap predicts stronger group identification

## Study 1

```{r}
tcomm.streng1 <-lmer(scale(streng) ~ scale(traitCommNod) + ( scale(traitCommNod) | subID) + (1 | id), data=idShort1)
summary(tcomm.streng1)
```

## Study 2

```{r}
tcomm.streng2 <-lmer(scale(streng) ~ scale(traitCommNod) + ( scale(traitCommNod) | subID) + (1 | id), data=idShort2)
summary(tcomm.streng2)
```

# More identity overlap predicts stronger group identification

## Study 1

```{r}
icomm.streng1 <-lmer(scale(streng) ~ scale(idCommNod) + ( scale(idCommNod) | subID) + (1 | id), data=idShort1)
summary(icomm.streng1)
```

## Study 2

```{r}
icomm.streng2 <-lmer(scale(streng) ~ scale(idCommNod) + ( scale(idCommNod) | subID) + (1 | id), data=idShort2)
summary(icomm.streng2)
```

# Individual Differences Predict Similarity in Identity Judgments

```{r}
m <-lmer(scale(posDist) ~ scale(SE.T2 - SE.T1)*Condition + ( scale(SE.T2 - SE.T1) | subID), data=idSim1)
summary(m)

m <-lmer(scale(strengDist) ~ scale(SE.T2 - SE.T1)*Condition + ( scale(SE.T2 - SE.T1) | subID), data=idSim1)
summary(m)

m <-lmer(scale(posDist) ~ scale(DS) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(posDist) ~ scale(SCC) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(posDist) ~ scale(MemSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(posDist) ~ scale(PrivCSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(posDist) ~ scale(PubCSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(posDist) ~ scale(MemSE) + ( 1 | subID), data=idSim1)
summary(m)
```

# Individual Differences Predict Pairwise Overlap in Traits in Common

## Study 1

### Positive

```{r}
m <-lmer(scale(idtpSim) ~ scale(SCC) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(Ind) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(Inter) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(SWLS) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(IdImp) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(phi) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(overlap_norm) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(H_index) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(SE) + scale(idtnSim) + ( scale(idtnSim)| subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(NFC) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(DS) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(SCC) + scale(idtnSim) + ( scale(idtnSim)| subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(MemSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(PrivCSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(PubCSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(MemSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim1)
summary(m)
```

### Negative

```{r}
m <-lmer(scale(idtnSim) ~ scale(SCC) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(Ind) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(Inter) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(SWLS) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(IdImp) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(phi) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(overlap_norm) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(H_index) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(SE) + scale(idtpSim) + ( scale(idtpSim)| subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(NFC) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(DS) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(SCC) + scale(idtpSim) + ( scale(idtpSim)| subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(MemSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(PrivCSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(PubCSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(MemSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim1)
summary(m)
```

### Both

```{r}
m <-lmer(scale(idtSim) ~ scale(SCC) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(Ind) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(Inter) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(SWLS) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(IdImp) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(phi) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(overlap_norm) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(H_index) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(SE) + ( 1| subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(NFC) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(DS) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(SCC) + ( 1| subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(MemSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(PrivCSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(PubCSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idtSim) ~ scale(MemSE) + ( 1 | subID), data=idSim1)
summary(m)
```

# Individual Differences Predict Pairwise Overlap in Identities in Common

```{r}
m <-lmer(scale(idSim) ~ scale(SCC) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(Ind) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(Inter) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(SWLS) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(IdImp) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(phi) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(overlap_norm) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(H_index) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(SE) + ( 1| subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(NFC) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(DS) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(SCC) + ( 1| subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(MemSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(PrivCSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(PubCSE) + ( 1 | subID), data=idSim1)
summary(m)

m <-lmer(scale(idSim) ~ scale(MemSE) + ( 1 | subID), data=idSim1)
summary(m)
```

## Study 2

### Positive

```{r}
m <-lmer(scale(idtpSim) ~ scale(SCC) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(Ind) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(Inter) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(SWLS) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(IdImp) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(phi) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(overlap_norm) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(H_index) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(SE) + scale(idtnSim) + ( scale(idtnSim)| subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(NFC) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(DS) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(SCC) + scale(idtnSim) + ( scale(idtnSim)| subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(MemSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(PrivCSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(PubCSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtpSim) ~ scale(MemSE) + scale(idtnSim) + ( scale(idtnSim) | subID), data=idSim2)
summary(m)
```

### Negative

```{r}
m <-lmer(scale(idtnSim) ~ scale(SCC) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(Ind) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(Inter) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(SWLS) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(IdImp) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(phi) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(overlap_norm) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(H_index) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(SE) + scale(idtpSim) + ( scale(idtpSim)| subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(NFC) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(DS) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(SCC) + scale(idtpSim) + ( scale(idtpSim)| subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(MemSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(PrivCSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(PubCSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtnSim) ~ scale(MemSE) + scale(idtpSim) + ( scale(idtpSim) | subID), data=idSim2)
summary(m)
```

### Both

```{r}
m <-lmer(scale(idtSim) ~ scale(SCC) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(Ind) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(Inter) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(SWLS) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(IdImp) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(phi) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(overlap_norm) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(H_index) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(SE) + ( 1| subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(NFC) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(DS) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(SCC) + ( 1| subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(MemSE) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(PrivCSE) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(PubCSE) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idtSim) ~ scale(MemSE) + ( 1 | subID), data=idSim2)
summary(m)
```

# Individual Differences Predict Pairwise Overlap in Identities in Common

```{r}
m <-lmer(scale(idSim) ~ scale(SCC) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(Ind) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(Inter) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(SWLS) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(IdImp) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(phi) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(overlap_norm) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(H_index) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(SE) + ( 1| subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(NFC) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(DS) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(SCC) + ( 1| subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(MemSE) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(PrivCSE) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(PubCSE) + ( 1 | subID), data=idSim2)
summary(m)

m <-lmer(scale(idSim) ~ scale(MemSE) + ( 1 | subID), data=idSim2)
summary(m)
```


# More trait overlap predicts more intergroup bias

## Study 2 Only

```{r}
m<-lmer(scale(interG) ~ scale(traitCommNod) + scale(idCommNod) + ( scale(traitCommNod) + scale(idCommNod) | subID) + ( 1  | id), data=idShort2)
summary(m)
```

# Identity Centrality Predicts Less Mutability

## Study 1 Only

```{r}
mall.I2I<-lmer(scale(mall) ~ scale(I2Ideg) + ( scale(I2Ideg) | subID) + ( 1  | id), data=idShort1)
summary(mall.I2I)
```

# Positivity of Identity Associated with Greater Intergroup Bias

## Study 2 Only

### More positive self-reported

```{r}
m<-lmer(scale(interG) ~ scale(pos) + ( scale(pos) | subID) + ( 1  | id), data=idShort2)
summary(m)
```

### More positive traits associated with identity than negative

```{r}
m<-lmer(scale(interG) ~ scale(pndiff) + ( scale(pndiff) | subID) + ( 1  | id), data=idShort2)
summary(m)
```

# Differentiation and Inclusion Quadratic Association

## Study 2 Only

```{r}
m<-lmer(scale(differ) ~ scale(poly(inclus, 2)) + ( scale(inclus) | subID) + ( 1  | id), data=idShort2[!is.na(idShort2$differ) & !is.na(idShort2$inclus), ])
summary(m)
ggpredict(m, c(  "inclus" )) %>% plot(show.title=FALSE)
```
# Differentiation and Inclusion Interact in Predicting Identification

## Study 2 Only

```{r}
m<-lmer(scale(streng) ~ scale(inclus) * scale(differ) + ( scale(inclus) + scale(differ) | subID) + ( 1  | id), data=idShort2)
summary(m)
ggpredict(m, c(  "inclus" , "differ")) %>% plot(show.title=FALSE)
```

```{r}
m<-lmer(scale(streng) ~ scale(poly(inclus, 2)) + scale(poly(differ, 2)) + ( scale(poly(inclus, 2)) + scale(poly(differ, 2)) | subID) + ( 1  | id), data=idShort2[!is.na(idShort2$differ) & !is.na(idShort2$inclus), ])
summary(m)
ggpredict(m, c(  "inclus[all]" , "differ[all]")) %>% plot(show.title=FALSE)
```

# Network Measures Correlated with External Measures

attempted in tidyverse

```{r}
# networkMeasures %>% map(~ .x) %>% select(indDiff1, SE:CESD, .)
# 
# selected<-map(networkMeasures, ~ select(indDiff1, SE:CESD, .) )
# map2(networkMeasures, ~ selected, networkMeasures )
```


## Study 1

```{r}
networkMeasures <- indDiff1 %>% select(matches("H_index"):matches("globEff")) %>% colnames(.)

for(i in 1:length(networkMeasures)){
  corsDf <- indDiff1 %>% select(SE:CESD, networkMeasures[i] ) %>% corToOne(., networkMeasures[i])
  barsDf <- indDiff1 %>% select(SE:CESD, networkMeasures[i] ) %>% plotCorToOne(., networkMeasures[i])
  
  assign(paste0(networkMeasures[i],".CorDf"),corsDf)
  assign(paste0(networkMeasures[i],".CorPlotDf"),barsDf)
  
  print(corsDf)
  print(barsDf)
}
```

## Study 2

```{r}
networkMeasures <- indDiff2 %>% select(matches("H_index"):matches("globEff")) %>% colnames(.)

for(i in 1:length(networkMeasures)){
  corsDf <- indDiff2 %>% select(SE:MC, networkMeasures[i] ) %>% corToOne(., networkMeasures[i])
  barsDf <- indDiff2 %>% select(SE:MC, networkMeasures[i] ) %>% plotCorToOne(., networkMeasures[i])
  
  assign(paste0(networkMeasures[i],".CorDf"),corsDf)
  assign(paste0(networkMeasures[i],".CorPlotDf"),barsDf)
  
  print(corsDf)
  print(barsDf)
}
```

# Normative Latino Ratings

```{r}
normTraits <- read.csv("~/Google Drive/Volumes/Research Project/Identity Feedback/Study 1/Data/Output/Normative/normativeDfStudy12.csv", header = T)
posTraits <- read.csv("~/Google Drive/Volumes/Research Project/Trait Network_Behaviral/generating network/output/allPosCents.csv")
negTraits <- read.csv("~/Google Drive/Volumes/Research Project/Trait Network_Behaviral/generating network/output/allNegCents.csv")
traits <- rbind(posTraits,negTraits)

fullLong1s <- fullLong1 %>% select(subID,id,idC,connect,traits,selfResp,IdIn,connect,streng)
fullLong2s <- fullLong2 %>% select(subID,id,idC,connect,traits,selfResp,IdIn,connect,streng)
fullLong2s$subID <- fullLong2$subID + 100000

combLong <- rbind(fullLong1s,fullLong2s)

combLong <- merge(combLong, normTraits, by = "traits")
combLong$ynLatin <- ifelse(combLong$idC==2 & combLong$id=="Race", "HL", "Not HL")
combLong$ynAsian <- ifelse(combLong$idC==4 & combLong$id=="Race", "As", "Not As")
combLong$ynMale <- ifelse(combLong$idC==1 & combLong$id=="Gen", "M", "Not M")
combLong$ynFemale <- ifelse(combLong$idC==2 & combLong$id=="Gen", "F", "Not F")
combLong$ynHetero <- ifelse(combLong$idC==1 & combLong$id=="Sex", "Het", "Not Het")
combLong$ynBis <- ifelse(combLong$idC==3 & combLong$id=="Sex", "Bi", "Not Bi")
combLong$ynCath <- ifelse(combLong$idC==1 & combLong$id=="Rel", "Cath", "Not Cath")
combLong$ynChrist <- ifelse(combLong$idC==2 & combLong$id=="Rel", "Christ", "Not Christ")
combLong$ynAgnos <- ifelse(combLong$idC==8 & combLong$id=="Rel", "Agn", "Not Agn")
combLong$ynAthei <- ifelse(combLong$idC==9 & combLong$id=="Rel", "Ath", "Not Ath")
combLong$ynDem <- ifelse(combLong$idC==1 & combLong$id=="Pol", "Dem", "Not Dem")
```

## Correlations

```{r}
traits <- rbind(posTraits,negTraits)
norms <- normTraits %>% select(Latino:Democrat)
traits <- cbind(traits,norms)
traitvars <- traits %>% select(desirability:prevalence, outDegree:inDegree)
cor(norms, traitvars)
```

## Latino

```{r}
raceLong <- subset(combLong, id == "Race")
m <- lmer( scale(selfResp) ~ scale(Latino)*ynLatin + ( scale(Latino) | subID) + ( 1 | traits), data = raceLong)
summary(m)
ggpredict(m, c("Latino", "ynLatin")) %>% plot()
```

## Asian

```{r}
m <- lmer( scale(selfResp) ~ scale(Asian)*ynAsian + ( scale(Asian) | subID) + ( 1 | traits), data = raceLong)
summary(m)
ggpredict(m, c("Asian", "ynAsian")) %>% plot()
```
## Female

```{r}
GenLong <- subset(combLong, id=="Gen")
m <- lmer( scale(selfResp) ~ scale(Female)*ynFemale + ( scale(Female) | subID) + ( 1 | traits), data = GenLong)
summary(m)
ggpredict(m, c("Female", "ynFemale")) %>% plot()
```

## Male

```{r}
m <- lmer( scale(selfResp) ~ scale(Male)*ynMale + ( scale(Male) | subID) + ( 1 | traits), data = GenLong)
summary(m)
ggpredict(m, c("Male", "ynMale")) %>% plot()
```

## Catholic

```{r}
RelLong <- subset(combLong, id=="Rel")
m <- lmer( scale(selfResp) ~ scale(Catholic)*ynCath + ( scale(Catholic) | subID) + ( 1 | traits), data = RelLong)
summary(m)
ggpredict(m, c("Catholic", "ynCath")) %>% plot()
```

## Christian

```{r}
m <- lmer( scale(selfResp) ~ scale(Christian)*ynChrist + ( scale(Christian) | subID) + ( 1 | traits), data = RelLong)
summary(m)
ggpredict(m, c("Christian", "ynChrist")) %>% plot()
```

## Atheist

```{r}
m <- lmer( scale(selfResp) ~ scale(Atheist)*ynAthei + ( scale(Atheist) | subID) + ( 1 | traits), data = RelLong)
summary(m)
ggpredict(m, c("Atheist", "ynAthei")) %>% plot()
```

## Agnostic

```{r}
m <- lmer( scale(selfResp) ~ scale(Agnostic)*ynAgnos + ( scale(Agnostic) | subID) + ( 1 | traits), data = RelLong)
summary(m)
ggpredict(m, c("Agnostic", "ynAgnos")) %>% plot()
```
## Democrat

```{r}
PolLong <- subset(combLong, id=="Pol")
m <- lmer( scale(selfResp) ~ scale(Democrat)*ynDem + ( scale(Democrat) | subID) + ( 1 | traits), data = PolLong)
summary(m)
ggpredict(m, c("Democrat", "ynDem")) %>% plot()
```


